Planning with Hierarchical Temporal Memory for Deterministic Markov Decision Problem

### 2020-12-19 reports/v1_0/paper_eng/paper_eng.tex
fix figure captions and positioning

\begin{figure}
  \centering
  \begin{minipage}{.49\linewidth}
    \includesvg[width=\linewidth]{gridworld_5x5_1_1_200_1337_map_0_1173222464}
  \end{minipage}
  \begin{minipage}{.49\linewidth}
    \includesvg[width=\linewidth]{gridworld_5x5_1_1_200_1337_map_2_1561234712}
  \end{minipage}
  \caption{Example of generated maze environments of 5x5 and 8x8 sizes. Walls - dark purple, starting agent's position - yellow, rewarding goal state - salad.} \label{fig_maze_examples}
\end{figure}

@@

  \caption{Episode durations (in steps) for handcrafted mazes \texttt{multi\_way\_v0} (a) and \texttt{multi\_way\_v2} (b). Our agent performed consistently better than random policy, and with enough planning horizon it performed better than DQN agent. Notice, how fast the agent with planning horizon $8$ learns the optimal path compared to the DQN agent.} \label{fig_comparison_mw}
\end{figure}

@@

  \caption{Episode durations (in steps) for the agent on \texttt{multi\_way\_v0} depending on how many rewarding goal states it can track - last 16 or just the last one - grouped by the planning horizon length.} \label{fig_detailed_mw0}
\end{figure}

@@

    % \includesvg[width=\linewidth]{gridworld_5x5_100_2_8_1337__dqn__steps}
    % \subcaption{Greedy and $\epsilon$-greedy DQN agent}
    % \vspace*{10pt}

    \includesvg[width=\linewidth]{gridworld_5x5_100_2_8_1337__2__steps}
    \subcaption{}
    % \vspace*{10pt}

    % \includesvg[width=\linewidth]{gridworld_5x5_100_2_8_1337__4-8__steps}
    % \subcaption{}
    \vspace*{4pt}
  \end{minipage}
  \caption{Episode durations for the experiment with rarely changed environments. a) Comparison with the baselines. Our agent with the planning horizon 8 performed the best. Each change of the environment configuration there's a spiked degradation of the performance for DQN agent, while our agents quickly relearn new position. b) Performance comparison for the different number of simultaneously tracked goals; planning horizon lengths are 4 and 8.} \label{fig_rare_changes}
\end{figure}

@@

@@

\begin{figure}
  \centering
  \begin{minipage}{.95\linewidth}
    \includesvg[width=\linewidth]{gridworld_5x5_20_1_20_1337__steps}
    \subcaption{}
    \vspace*{10pt}

    % \includesvg[width=\linewidth]{gridworld_5x5_20_1_20_1337__dqn__steps}
    % \subcaption{Greedy and $\epsilon$-greedy DQN agent}
    % \vspace*{10pt}

    \includesvg[width=\linewidth]{gridworld_5x5_20_1_20_1337__2__steps}
    \subcaption{}
    % \vspace*{10pt}

    % \includesvg[width=\linewidth]{gridworld_5x5_20_1_20_1337__4-8__steps}
    % \subcaption{}
    \vspace*{4pt}
  \end{minipage}

  \caption{Episode durations for the experiment with frequently changed environments. a) Comparison with the baselines. Our method performed more stable with small planning horizons (1-4), while with planning horizon 8 it performed either very good or very bad. DQN agent results were worse than of random policy - the frequency of changes was too high for it to adapt before the next change. b) Comparison for the different number of simultaneously tracked goals; planning horizon lengths are 4 and 8.} \label{fig_frequent_changes}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{minipage}{.49\linewidth}
    \includesvg[width=\linewidth]{gridworld_5x5_1_1_200_1337_map_0_1173222464}
  \end{minipage}
  \begin{minipage}{.49\linewidth}
    \includesvg[width=\linewidth]{gridworld_5x5_1_1_200_1337_map_2_1561234712}
  \end{minipage}
  \caption{Two examples of generated 5x5 maze environments. Walls - dark purple, starting agent's position - yellow, rewarding goal state - salad.} \label{fig_maze_examples}
\end{figure}

@@

  \caption{Episode durations (in steps) for handcrafted mazes \texttt{multi\_way\_v0} (a) and \texttt{multi\_way\_v2} (b). Results are shown with the moving average 20. Our agent performed consistently better than pure random policy, and with enough planning horizon it performed better than DQN agent. Notice, how fast the agent with the planning horizon $8$ learns an optimal path compared to the DQN agent.} \label{fig_comparison_mw}
\end{figure}

@@

  \caption{Episode durations (in steps) for the agent on \texttt{multi\_way\_v0} depending on how many rewarding goal states it can track - last 16 or just the last one - grouped by the planning horizon length. Results are shown with the moving average 20.} \label{fig_detailed_mw0}
\end{figure}

@@

    \includesvg[width=\linewidth]{gridworld_5x5_100_2_8_1337__2__steps}
    \subcaption{}
    \vspace*{4pt}
  \end{minipage}
  \caption{Episode durations for the experiment with rarely changed environments. Results are shown with the moving average 40. a) Comparison with the baselines. Our agent with the planning horizon 8 performed the best. Notice, how an each change of the environment configuration results in a spiked degradation of the performance for DQN agent, while our agent quickly relearns new position. b) Performance comparison for the different number of simultaneously tracked goals - the last goal or last 4; planning horizon length = 2. } \label{fig_rare_changes}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \includesvg[width=\linewidth]{gridworld_5x5_20_1_20_1337__steps}
    \subcaption{}
    \vspace*{10pt}

    \includesvg[width=\linewidth]{gridworld_5x5_20_1_20_1337__2__steps}
    \subcaption{}
    \vspace*{4pt}
  \end{minipage}

  \caption{Episode durations for the experiment with frequently changed environments. Results are shown with the moving average 40. a) Comparison with the baselines. Our method performed more stable with small planning horizons (1-4), while with planning horizon 8 it performed either very good or very bad. DQN agent results were worse than of random policy - the frequency of changes was too high for it to adapt before the next change. b) Comparison for the different number of simultaneously tracked goals; planning horizon length = 2.} \label{fig_frequent_changes}
\end{figure}

@@
